Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2013-05-08 paper.tex
add figs
add some more gravity

@@

>>>>

\subsection{Gravity}

To properly describe the gravitational potential for the system, we need 
isolated boundary conditions.  The adaptive gravity solve in Castro 
is described in \cite{castro}, and consists of both level and composite
solves, and a final synchronization at the end.  To implement isolated
boundary conditions, we make the simplying assumption that only level
0 grids will touch the boundary of our computational domain.

Figure~\ref{fig:2levgrav} shows the sequence of updates for $\phi$
on a 2-level grid.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.1in]{nested2}\hspace{1em}
  \includegraphics[width=3.1in]{nested3}
  \caption{\label{fig:2levgrav} Schematic showing the solve for $\phi$ for a 2-level grid.}
\end{figure}
